### 2021-03-02 phd_2/article/article.tex
experiment drawing to b\w
remove 3rd pic

    \begin{figure}[H]
        \centering
        \subfloat[Температурное поле на $\Gamma$]
            { \label{fig:theta_b} \includegraphics[width=.49\linewidth]{img/exp2/theta_b} }
        \subfloat[Производная по нормали]
        { \label{fig:theta_n} \includegraphics[width=.49\linewidth]{img/exp2/theta_n} }
        \caption{Графики температурного поля $\theta$}
    \end{figure}

>>>>

    \begin{figure}[H]
        \centering
        { \label{fig:theta_n} \includegraphics[width=.49\linewidth]{img/exp2/theta_n} }
        \caption{Графики температурного поля $\theta$}
    \end{figure}
